### 2019-04-10 5_evaluation.tex
Add note about Regent and X10 results.

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs. Some slower systems
are omitted from comparisons with more complicated dependence
patterns, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6 hours) to reach 50\% efficiency.

>>>>

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs.

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependence
patterns, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency. Regent and X10 are missing from some
graphs as Cori was highly impacted before the deadline.
